---
title: "Grapher"
bibliography: "bibliography.bib"
nocite: |
     @*
format:
    html:
     theme: superhero
     fig-format: retina
     fig-dpi: 600
     fig-height: 6
     fig-width: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina=3, fig.width = 9, fig.height=6, warning = FALSE, message = FALSE, dev.args = list(jpeg = list(type = "cairo")), type="cairo")
library(tidyverse)
library(gt)
library(gtExtras)
library(Cairo)
library(svglite)
```

There is commented code for loading in each of the three data files.  I have combined them and mutated them because it is a long operation.

```{r}
library(magrittr)
load("Complete.Data.01.2026.RData")
```


A few objectives.

- It occurred to me that we do not really make use of the *discrete* tag.  I will in this document in a moment.  

## Fresh.Outcome

I have recreated the outcomes below in a variable called `Fresh.Outcome`.  We should be careful about how these are recoded to be both transparent about what it does and for our clarity in reporting.  Here is that table.

```{r}
Complete.Data.01.2026$Fresh.Outcome <- c(1:196000) %>% map_chr(., function(x) {Complete.Data.01.2026$response$body$choices[[x]]$message$content})
Complete.Data.01.2026$model <- Complete.Data.01.2026$body$model
Complete.Data.01.2026 <- Complete.Data.01.2026 |> mutate(modelF = factor(model, levels = c('gpt-4-turbo-2024-04-09', 'gpt-4-0613', 'gpt-4o-2024-08-06', 'gpt-5.2-2025-12-11')))
Complete.Data.01.2026 |> group_by(Fresh.Outcome, model) |> summarise(Count = n()) |>  ungroup() |> pivot_wider(names_from = model, values_from = Count) |> gt()
```

I am going to recreate the `Outcome` variable as follows.

```{r}
Complete.Data.01.2026 <- Complete.Data.01.2026 |> 
  mutate(Outcome = case_match(Fresh.Outcome, 
                              c("arcsine","Arcsine") ~ "Arcsine",
                              c("categorical","Categorical") ~ "Categorical",
                              c("exponential","Exponential") ~ "Exponential",
                              c("beta","Beta") ~ "Beta",
                              c("Chisquare","Chi-Square") ~ "Chi-square",
                              c("exgaussian","ExGaussian") ~ "ExGaussian",
                              c("Normal","normal") ~ "Normal",
                              c("binomial","Binomial") ~ "Binomial",
                              c("geometric","Geometric") ~ "Geometric",
                              c("gamma","Gamma") ~ "Gamma",                              c("Lognormal","lognormal","Log-Normal","Log-normal") ~ "Lognormal",
                              c("NegativeBinomial","Negative Binomial","NegBinomial","Negbinomial","negativebinomial","Negativebinomial") ~ "Negative Binomial",
                              c("Skewed","Skewnormal","SkewNormal","Skew-normal","Skew-right","Skewness","skewnormal")~ "Skewed",
                              c("Student","Studentt","Studentt","t")~ "Student's t", c("Uniform","uniform")~ "Uniform",
                              c("ZeroInflatedPoisson","ZeroinflatedPoisson","Zero-inflated","ZIP")~ "ZIP",
                              .default = Fresh.Outcome))
# Complete.Data |> group_by(Outcome, model) |> summarise(Count = n()) |>  ungroup() |> pivot_wider(names_from = model, values_from = Count) |> gt()
```

## The `discrete` tag

```{r}
Complete.Data.01.2026 <- Complete.Data.01.2026 |> mutate(Type = case_match(name, c("Binomial","Geometric","Poisson") ~ "Discrete", .default = "not Discrete"))
Complete.Data.01.2026 <- Complete.Data.01.2026 |> mutate(Correct = as.character(name==Outcome)) |> mutate(Correct = case_match(Correct, "TRUE" ~ "Correct", .default = "Incorrect"))
```

## Basic Percent Correctly Predicted

```{r}
MNTotals <- Complete.Data.01.2026 |> group_by(model, name) |> summarise(Total = n()) |> ungroup()
PCP <- Complete.Data.01.2026 |> group_by(model, name, Correct) |> summarise(count = n()) |> ungroup()
PCPTab <- left_join(PCP, MNTotals) |> filter(Correct=="Correct") |> mutate(PCP = count / Total) |> select(model, name, PCP)
PCPTab
```




## The Plot

```{r DTAP1, fig.width=9, fig.height=6, dpi=300}
Tab.All <- Complete.Data.01.2026 |> group_by(model, name, Outcome) |> summarise(Count = n()) |> ungroup() |> group_by(model,name) |> mutate(Total = sum(Count)) |> ungroup() |> mutate(PCP = round(Count / Total, digits=3)) |> ungroup()
TAP1 <- Tab.All |> ggplot() + aes(x=Outcome, y=fct_rev(name), fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="True Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(legend.location = "plot", panel.spacing = unit(2, "lines"), plot.label= element_text(size=5), plot.title=element_text(size=10, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(size=8)) + 
    theme(legend.position="bottom", legend.direction = "horizontal") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + scale_x_discrete(position="top", guide = guide_axis(n.dodge = 2)) +
    theme(
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 8),
        legend.key.width = unit(0.15, "in"),
        legend.position = c(0.15, 0.69)
    )
TAP1
```


```{r BL, fig.width=9, fig.height=6, dpi=300}
TAP1BL <- Tab.All |> ggplot() + aes(x=Outcome, y=fct_rev(name), fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="True Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(legend.location = "plot", panel.spacing = unit(2, "lines"), plot.label= element_text(size=5), plot.title=element_text(size=10, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(size=8)) + 
    theme(legend.position="bottom", legend.direction = "horizontal") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + scale_x_discrete(position="top", guide = guide_axis(n.dodge = 2)) +
    theme(
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 8),
        legend.key.width = unit(0.15, "in"),
        legend.position = c(0, -0.06)
    )
TAP1BL
ggsave(filename = "Final-Table-BotLLeg.jpeg", TAP1BL)
```



```{r T1TR, fig.width=9, fig.height=6, dpi=300, dev='CairoJPEG'}
TAP1TR <- Tab.All |> ggplot() + aes(x=Outcome, y=fct_rev(name), fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="True Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(legend.location = "plot", panel.spacing = unit(2, "lines"), plot.label= element_text(size=5), plot.title=element_text(size=10, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(size=8)) + 
    theme(legend.position="bottom", legend.direction = "horizontal") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + scale_x_discrete(position="top", guide = guide_axis(n.dodge = 2)) +
    theme(
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 8),
        legend.key.width = unit(0.15, "in"),
        legend.position = c(0.9, 1.12)
    )
TAP1TR
```



```{r DTAP2, fig.width=9, fig.height=6, dpi=300, type='cairo'}
TAP2 <- Tab.All |> ggplot() + aes(x=Outcome, y=fct_rev(name), fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="True Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(legend.location = "plot", panel.spacing = unit(2, "lines"), plot.label= element_text(size=5), plot.title=element_text(size=10, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(size=8)) + 
    theme(legend.position="bottom") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + scale_x_discrete(position="top", guide = guide_axis(n.dodge = 2)) + 
  theme(
    legend.text = element_text(size = 6), 
    legend.title = element_text(size = 8),
    legend.key.width = unit(0.15, "in"),
    legend.position = c(0.4, 0.8)
    )
TAP2
```



### A go at Discrete

```{r DDT1, fig.width=8, fig.height=6, dpi=900}
Data.Disc.Tab <- Complete.Data.01.2026 |> filter(Type=="Discrete") |> group_by(model, name, Outcome) |> summarise(Count = n()) |> ungroup() |> group_by(model,name) |> mutate(Total = sum(Count)) |> ungroup() |> mutate(PCP = round(Count / Total, digits=3)) |> ungroup()
TableDisc <- Data.Disc.Tab |> ggplot() + aes(x=Outcome, y=fct_rev(name), fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="a", subtitle="Discrete Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(plot.label= element_text(size=5), plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(angle = 25)) + 
    theme(legend.position="bottom") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + scale_x_discrete(position="top") + guides(fill=FALSE)
TableDisc
```

```{r DHT1}
TabPCPDisc <- Complete.Data.01.2026 |> filter(Type=="Discrete") |> ggplot() + aes(y=name, fill=as.character(Correct), facet=model) + geom_bar(position="fill", alpha=0.4) + 
    scale_fill_viridis_d(option = "E", alpha=0.4, direction = 1) + 
    labs(y="True Distribution", x="Model Outcome") + labs(title="b", subtitle="True Discrete Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot") + theme(legend.position="bottom") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + guides(fill=FALSE)
TabPCPDisc
```

```{r Pat1}
library(patchwork)
TableDisc + TabPCPDisc + plot_layout(widths=c(5,2))
```

## Not Discrete

```{r, fig.width=8, fig.height=6, dpi=900}
Complete.Data.01.2026 |> filter(Type=="not Discrete") |> group_by(model, name, Outcome) |> summarise(Count = n()) |> ungroup() |> group_by(model,name) |> mutate(Total = sum(Count)) |> ungroup() |> mutate(PCP = round(Count / Total, digits=3)) |> ungroup() -> TableDatanD
TableNDisc <- TableDatanD |> ggplot() + aes(x=Outcome, y=fct_rev(name), fill=PCP, facet=model) +
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="c", subtitle="Continuous Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(plot.label= element_text(size=5), plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(angle = 25)) + 
    theme(legend.position="bottom") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + scale_x_discrete(position="top") + guides(fill=FALSE)
TableNDisc
```

```{r nDHT1}
TabPCPnDisc <- Complete.Data.01.2026 |> filter(Type=="not Discrete") |> ggplot() + aes(y=name, fill=as.character(Correct), facet=model) + geom_bar(position="fill", alpha=0.4) + 
    scale_fill_viridis_d(option = "E", alpha=0.4, direction = 1) + 
    labs(y="True Distribution", x="Model Outcome") + labs(title="d", subtitle="Continuous Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot") + theme(legend.position="bottom") + facet_wrap(vars(model), nrow = 3, strip.position = "bottom") + guides(fill=FALSE)
TabPCPnDisc
```

## A Combined Patchwork

```{r, fig.width=8, fig.height=8, dpi=600}
design <- c(area(1,1,4,5),area(1,6,4,8), area(5,1,8,5),area(5,6,8,8))
My.Graph <- (TableDisc + TabPCPDisc) / (TableNDisc + TabPCPnDisc) + plot_layout(guides='collect', design=design, nrow = 2, ncol=2) + theme(legend.position = "bottom")
My.Graph
ggsave(filename = "CoolPlot.png", My.Graph, dpi=600, dev = png, type="cairo", width=9, height=6, units = "in")
```


# gpt4-0613

```{r}
Tab1.1 <- Complete.Data.01.2026 |> filter(model=="gpt-4-0613") %$% 
  table(name, Outcome) %>% 
  data.frame() %>% group_by(name) %>% 
  mutate(Count = sum(Freq)) %>% ungroup() |> 
  mutate(Percent = round(Freq / Count, digits=3)) |> 
  ggplot() + aes(x=as.character(name), y=as.character(fct_rev(Outcome)), fill=Percent) + 
  geom_tile(alpha=0.4) + 
  scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
  labs(x="True Distribution", y="gpt-4-0613 Outcome") + geom_text(aes(label=Percent), color="black") + labs(caption="Values are column percents", title="True Distributions and Model Responses", fill="Col. Pct.") + theme_minimal() + theme(plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(angle = 45)) + 
  theme(legend.position="bottom")

Tab2.1 <- Complete.Data.01.2026 |> filter(model=="gpt-4-0613") |> group_by(name) |> mutate(Correct = (name==Outcome)) |> ggplot() + aes(x=name, fill=Correct) + geom_bar(position = "fill", alpha=0.4) + scale_fill_viridis_d(option="E", direction=-1) + theme_minimal() + labs(x="True Distribution", y="Percent Correct", title="b", subtitle="Correct Prediction: gpt-4-0613")+ theme(text = element_text(size = 10, family="helvetica"), plot.title = element_text(family="helvetica", face="bold"), plot.title.position = "plot", plot.subtitle = element_text(size=12, family="helvetica"))

Tab3.1 <- Complete.Data.01.2026 |> filter(model=="gpt-4-0613") |> mutate(Correct = (name==Outcome)) |> ggplot() + aes(y=Outcome, fill=Correct) + geom_bar(alpha=0.4, show.legend = FALSE, position = "stack") + scale_fill_viridis_d(option="E", direction=-1) + theme_minimal() + labs(y="gpt-4-0613 Outcome", x="Frequency Chosen", title="c", subtitle="True and False Responses: gpt-4-0613") + theme(text = element_text(size = 10, family="helvetica"), plot.title=element_text(family="helvetica", size=12, face="bold"), plot.title.position = "plot") + theme(legend.position="bottom")

Tab4.1 <- Complete.Data.01.2026 |> filter(model=="gpt-5.2-2025-12-11") |> mutate(Correct = (name==Outcome)) |> ggplot() + aes(y=Outcome, fill=Correct) + geom_bar(alpha=0.4, show.legend = FALSE, position = "stack") + scale_fill_viridis_d(option="E", direction=-1) + theme_minimal() + labs(y="gpt-4-0613 Outcome", x="Frequency Chosen", title="c", subtitle="True and False Responses: gpt-4-0613") + theme(text = element_text(size = 10, family="helvetica"), plot.title=element_text(family="helvetica", size=12, face="bold"), plot.title.position = "plot") + theme(legend.position="bottom")
```

# A third patchwork

```{r}
design <- c(area(1,1,4,4),area(1,5,4,6), area(5,1,6,4),area(5,5,6,6))
Tab1.1 + Tab3.1 + Tab2.1 + guide_area()+ plot_layout(design=design, guides = "collect") -> Plot3
ggsave("Plot0613A.jpeg", Plot3)
```

# Others

```{r}
Complete.Data.01.2026 |> ggplot() + aes(y=Outcome, fill=Correct, group=model) + geom_bar(position="fill") + facet_grid(rows=vars(name), cols=vars(model), scales = "free")  + theme_minimal() + scale_fill_viridis_d(option = "E") -> Simples
ggsave("Simples.jpeg", Simples, dpi=600)
```

```{r}
Complete.Data.01.2026 |> ggplot() + aes(y=name, fill=Correct) + geom_bar(position="fill", alpha=0.4) + facet_grid(cols=vars(model), scales = "free")  + theme_minimal() + scale_fill_viridis_d(option = "E") + labs(title="a", x="Percent", y="True Distribution", subtitle="Percent Correctly Predicted") + theme(plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", legend.position="bottom") -> Plot1A
Plot1A
```

```{r}
Complete.Data.01.2026 |> mutate(NormPoisU = as.character(Outcome %in% c("Uniform","Normal","Poisson"))) |> ggplot() + aes(y=Outcome, fill=Correct) + geom_bar(position="dodge", alpha=0.4) + facet_grid(cols=vars(model), rows=vars(NormPoisU), scales = "free")  + theme_minimal() + scale_fill_viridis_d(option = "E") + labs(title="b", x="Percent", y="Model Outcome", subtitle="Model Outcomes") + theme(plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", legend.position="bottom") -> Plot1B
Plot1B
```


```{r}
Complete.Data.01.2026 |> ggplot() + aes(y=Outcome, fill=Correct) + geom_bar(position="dodge", alpha=0.4) + facet_grid(cols=vars(model), scales = "free")  + theme_minimal() + scale_fill_viridis_d(option = "E") + labs(title="b", x="log_10", y="Model Outcome", subtitle="Model Outcomes") + theme(plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", legend.position="bottom") + scale_x_log10() -> Plot1B1
Plot1B1
```

```{r}
Complete.Data.01.2026 %$% table(model, name, Outcome, Correct) %>% data.frame() |> ggplot() + aes(y=Outcome, x=Freq, fill=Correct) + geom_col(position="fill") + facet_grid(cols=vars(model))
```

```{r}
Complete.Data.01.2026 %$% table(model, name, Outcome, Correct) %>% data.frame() |> ggplot() + aes(y=Outcome, x=Freq, fill=Correct) + geom_col(position="dodge") + facet_grid(cols=vars(model)) + scale_x_sqrt() + scale_fill_viridis_d(option = "E") + theme_minimal()
```

```{r}
library(janitor)
DTab <- Complete.Data.01.2026 |> group_by(model, name, Outcome, Correct) |> summarise(Count = n()) |> ungroup() |> group_by(model, name) |> mutate(Total = sum(Count)) |> ungroup() |> mutate(PCP = Count / Total)
```

```{r, eval=FALSE}
TableData |> ggplot() + aes(y=as.character(Outcome), x=as.character(fct_rev(name)), fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_viridis_c(option = "E", alpha=0.4, direction = -1) + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), color="black") + labs(caption="Values are column percents", title="a", subtitle="True Distributions and Model Responses", fill="Col. Pct.") + theme_minimal() + theme(plot.label= element_text(size=5), plot.title=element_text(size=12, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(angle = 45)) + 
    theme(legend.position="bottom") + facet_wrap(vars(model), ncol = 3)
```


```{r, eval=FALSE}
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize), 
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

# Apply on original plot
addSmallLegend(p)
```

## Black and White

```{r}
Tab.All |> ggplot() + aes(y=fct_rev(Outcome), x=name, fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_continuous(palette = "Greys") + 
    labs(y="True Distribution", x="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=3, color="black") + labs(caption="Values are row percents", title="Known Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(legend.location = "plot", panel.spacing = unit(1, "lines"), plot.label= element_text(size=5), plot.title=element_text(size=10, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(size=8, angle=30), axis.text.y = element_text(size=7)) + 
    theme(legend.position="bottom", legend.direction = "horizontal") + facet_wrap(vars(model))  +
    theme(
        legend.text = element_text(size = 6), 
        legend.title = element_text(size = 8),
        legend.key.width = unit(0.15, "in"),
        legend.position = c(-0.075, -0.075)
    ) 
```

## Final Figure

```{r}
Tab.All |> ggplot() + aes(y=fct_rev(Outcome), x=name, fill=PCP, facet=model) + 
    geom_tile(alpha=0.4) + 
    scale_fill_continuous(palette = "Greys") + 
    labs(x="Known Distribution", y="Model Outcome") + geom_text(aes(label=round(PCP, digits=2)), size=2, color="black") + labs(caption="Values are row percents", title="Known Distributions and Model Responses", fill="Row. Pct.") + theme_minimal() + theme(legend.location = "plot", panel.spacing = unit(0.5, "lines"), plot.label= element_text(size=5), plot.title=element_text(size=10, face = "bold", hjust=0), plot.title.position = "plot", axis.text.x = element_text(size=8, angle=30), axis.text.y = element_text(size=5)) + 
    theme(legend.position="bottom", legend.direction = "horizontal") + facet_wrap(vars(model))  +
    theme(
        legend.text = element_text(size = 4), 
        legend.title = element_text(size = 6),
        legend.key.width = unit(0.1, "in"),
        legend.position = c(-0.06, -0.1)
    ) -> FinalFig
ggsave(FinalFig, dpi=900, device = "pdf", filename = "./FinalFigure.pdf", width=6.5, height=5.5, units = "in")
```

```{r}
my_greys <- colorRampPalette(c("grey100", "grey60"))(40)

library(rasterpdf)
Tab.All <- Tab.All |> mutate(modelF = factor(model, levels = c('gpt-4-turbo-2024-04-09', 'gpt-4-0613', 'gpt-4o-2024-08-06', 'gpt-5.2-2025-12-11'))) |> mutate(Dist.Match = (name==Outcome))

raster_pdf("./fully_rasterized_plot.pdf", width = 6.5, height = 6.5, res = 900) 

  ggplot(Tab.All) + 
  aes(y=fct_rev(Outcome), x=name, fill=PCP, facet=modelF) + 
  geom_tile(aes(color=Dist.Match), lwd=0.2, width=0.95, height=0.95) + 
  scale_color_manual(values = c("white","black")) + 
  guides(color="none") +
  scale_fill_gradientn(colors = my_greys) + 
  labs(x="Known Distribution", y="Model Outcome") +
  geom_text(aes(label=round(PCP, digits=2)), size=2, color="black") +
  labs(caption="Values are row percents", title="Known Distributions and Model Responses", fill="Row. Pct.") + 
  theme_minimal() + 
  theme(legend.location = "plot", 
        panel.spacing = unit(0.5, "lines"), 
        plot.label= element_text(size=5), 
        plot.title=element_text(size=10, face = "bold", hjust=0),
        plot.title.position = "plot", 
        axis.text.x = element_text(size=8, angle=30), 
        axis.text.y = element_text(size=5), 
        legend.direction = "horizontal",
        legend.text = element_text(size = 4), 
        legend.title = element_text(size = 6),
        legend.key.width = unit(0.1, "in"),
        legend.position = c(0.0, -0.1)
) +
    facet_wrap(vars(modelF), scales="free_y")

  dev.off()
```

```{r}
raster_pdf("./fully_rasterized_plot-FullY.pdf", width = 6.5, height = 6.5, res = 900) 

  ggplot(Tab.All) + 
  aes(y=fct_rev(Outcome), x=name, fill=PCP, facet=modelF) + 
  geom_tile(aes(color=Dist.Match), alpha=0.4, lwd=0.2, width=0.95, height=0.95) +   scale_fill_continuous(palette = "Greys") + 
  scale_color_manual(values = c("white","black")) + 
  guides(color="none") +
  labs(x="Known Distribution", 
       y="Model Outcome", 
       caption="Values are row percents", 
       title="Known Distributions and Model Responses", 
       fill="Row. Pct.") +
  geom_text(aes(label=round(PCP, digits=2)), size=1.4, color="black") +
  theme_minimal() + 
  theme(legend.location = "plot", 
        panel.spacing = unit(0.5, "lines"), 
        plot.label= element_text(size=5), 
        plot.title=element_text(size=10, face = "bold", hjust=0),
        plot.title.position = "plot", 
        axis.text.x = element_text(size=8, angle=30), 
        axis.text.y = element_text(size=5), 
        legend.direction = "horizontal",
        legend.text = element_text(size = 4), 
        legend.title = element_text(size = 6),
        legend.key.width = unit(0.1, "in"),
        legend.position = c(0.0, -0.1)
) +
    facet_wrap(vars(modelF))

  dev.off()
```

```{r}
FF2 <-   ggplot(Tab.All) + 
  aes(y=fct_rev(Outcome), x=name, fill=PCP, facet=modelF) + 
  geom_tile(aes(color=Dist.Match), lwd=0.2, width=0.95, height=0.95) + 
  scale_color_manual(values = c("white","black")) + 
  guides(color="none") +
  scale_fill_gradientn(colors = my_greys) + 
  labs(x="Known Distribution", y="Model Outcome") +
  geom_text(aes(label=round(PCP, digits=2)), size=2, color="black") +
  labs(caption="Values are row proportions", title="Known Distributions and Model Responses", fill="Row. Pct.") + 
  theme_minimal() + 
  theme(legend.location = "plot", 
        panel.spacing = unit(0.5, "lines"), 
        plot.label= element_text(size=5), 
        plot.title=element_text(size=10, face = "bold", hjust=0),
        plot.title.position = "plot", 
        axis.text.x = element_text(size=8, angle=30), 
        axis.text.y = element_text(size=5), 
        legend.direction = "horizontal",
        legend.text = element_text(size = 4), 
        legend.title = element_text(size = 6),
        legend.key.width = unit(0.1, "in"),
        legend.position = c(0.0, -0.1)
) +
    facet_wrap(vars(modelF), scales="free_y")
ggsave("FinalFigureFreeY.jpeg", FF2, width=6.5, height=6.5, dpi=900, units="in")
```


# References

```{r}
knitr::write_bib(names(sessionInfo()$otherPkgs), file="bibliography.bib")
```
