---
title: "Complete Data Summary"
format: html
---

## Collate Complete Files

This section collects the four distinct results sets and binds them together.

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(gtExtras)
load("~/Nextcloud/LLM_Distributions/Final-Prompt-Results/Complete.Data.All.0409.RData")
load("~/Nextcloud/LLM_Distributions/Final-Prompt-Results/Complete.Data.All.0613.RData")
load("~/Nextcloud/LLM_Distributions/Final-Prompt-Results/Complete.Data.All.0806.RData")
load("~/Nextcloud/LLM_Distributions/Final-Prompt-Results/Complete.Data.All.1211.RData")
Complete.Data.01.2026 <- bind_rows(Complete.Data.0409, Complete.Data.0613, Complete.Data.0806, Complete.Data.1211)
```


## Results

A first table of pure raw responses comes next.  This provides the foundation for cleaning up similar labels with variation in spelling and capitalization.

```{r FirstTab}
Complete.Data.01.2026$Fresh.Outcome <- c(1:196000) %>% map_chr(., function(x) {Complete.Data.01.2026$response$body$choices[[x]]$message$content})
Complete.Data.01.2026$model <- Complete.Data.01.2026$body$model
Complete.Data.01.2026 |> group_by(Fresh.Outcome, model) |> summarise(Count = n()) |>  ungroup() |> pivot_wider(names_from = model, values_from = Count) |> gt()
```

## Cleaned a bit

This is the minimal table with cleaned responses.  It is still far too large for usefulness.

```{r CleanTab, message=FALSE, warning=FALSE}
Complete.Data.01.2026 <- Complete.Data.01.2026 |> 
  mutate(Outcome = case_match(Fresh.Outcome, 
                              c("arcsine","Arcsine") ~ "Arcsine",
                              c("categorical","Categorical") ~ "Categorical",
                              c("exponential","Exponential") ~ "Exponential",
                              c("beta","Beta") ~ "Beta",
                              c("exgaussian","ExGaussian") ~ "ExGaussian",
                              c("Normal","normal") ~ "Normal",
                              c("binomial","Binomial") ~ "Binomial",
                              c("geometric","Geometric") ~ "Geometric",
                              c("gamma","Gamma") ~ "Gamma",                              c("Lognormal","lognormal","Log-Normal","Log-normal") ~ "Lognormal",
                              c("NegativeBinomial","Negative Binomial","NegBinomial","Negbinomial","negativebinomial","Negativebinomial") ~ "Negative Binomial",
                              c("Skewed","Skewnormal","SkewNormal","Skew-normal","Skew-right","Skewness","skewnormal")~ "Skewed",
                              c("Student","Studentt","Studentt","t")~ "Student's t", c("Uniform","uniform")~ "Uniform",
                              c("ZeroInflatedPoisson","ZeroinflatedPoisson","Zero-inflated","ZIP")~ "ZIP",
                              .default = Fresh.Outcome))
Complete.Data.01.2026 |> group_by(Outcome, model) |> summarise(Count = n()) |>  ungroup() |> pivot_wider(names_from = model, values_from = Count) |> gt()
```
